### 2017-04-17 paper/evaluation.tex
Added note about flaky projects and fixed label in Fig9

As of March 25th 2017, our search criteria returned \SubjectsGithub{}
subjects. Figure~\ref{fig:subjects} summarizes our sample set. From
\SubjectsGithub{} downloaded projects, \SubjectsGithubNotMaven{}
projects were not Maven or did not have a \pomf{} in the root
directory, \SubjectsGithubNotTestable{} projects were untestable
(because of missing dependencies or incompatible testing environment,
for example), and \SubjectsGithubFlaky{} projects were ``flaky''.  We
executed each project's test suite for three times to identify
projects containing flaky tests that could introduce noise in our
experiments.  Our final set of subjects consists of \numSubjs{}
projects.

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.25\textwidth]{plots/subjs.pdf}
    \caption{\label{fig:subjects}We fetched \SubjectsGithub{} popular
    projects hosted on \github{}. From this initial sample, we ignored
    \SubjectsGithubNotMaven{} projects without Maven support,
    \SubjectsGithubNotTestable{} untestable projects, and
    \SubjectsGithubFlaky{} projects with flaky tests. We considered
    \numSubjs{} projects to conduct our study.}
\end{figure}

@@

\begin{figure}[h!]
\centering
\resizebox{.48\textwidth}{!}{%
\begin{tabular}{llrrl}
\toprule
\emph{Group} & \emph{Subject} & \multicolumn{1}{c}{$T_s$} & \multicolumn{1}{c}{$T_p$} & $T_s/T_p$ \\%
\midrule%
Medium & BounceStorage \textbf{Chaos} HTTP Proxy  & 1.51m & 1.47m & 
    \cellcolor{lightgray}1.02x\\%
Medium & Apache \textbf{Flink} & 11.79m & 2.57m & 4.59x\\%
Long & Jenkins CI \textbf{Gerrit} Plugin & 51.19m & 40.31m &  1.26x\\%
Medium & Spotify \textbf{Helios} & 4.46m & 1.63m & 2.73x\\%  
Medium & \textbf{Javaslang} & 2.18m & 1.82m & 1.19x\\%
Medium & \textbf{Jcabi} GitHub & 2.76m & 0.30m &
    \cellcolor{lightgray}9.2x\\%
Medium & Hazelcast \textbf{Jet} & 8.26m & 3.67m & 2.25x\\%
Medium & Apache \textbf{Log4J2} & 8.24m & 8.21m & 
    \cellcolor{lightgray}1.00x\\%
Medium & Jankotek \textbf{MapDB} & 10.06m & 8.58m & 1.17x\\%
\midrule
\textbf{total} &  &  &  & \avgSpeedup{}x\\
\bottomrule%
\end{tabular}}
\caption{Speedup (or slowdown) of parallel execution ($T_p$) over
  sequential execution ($T_s$).  Default parallel configuration of
  Maven is used.  Abbreviation of project names appear in bold face
  and highest slowdown/speedup appear in gray color.}
\label{tab:speedup}
\end{figure}

>>>>

As of March 25th 2017, our search criteria returned \SubjectsGithub{}
subjects. Figure~\ref{fig:subjects} summarizes our sample set. From
\SubjectsGithub{} downloaded projects, \SubjectsGithubNotMaven{}
projects were not Maven or did not have a \pomf{} in the root
directory, \SubjectsGithubNotTestable{} projects were untestable
(because of missing dependencies or incompatible testing environment,
for example), and \SubjectsGithubFlaky{} projects were ``flaky''.
\Jbc{Check if this is ok $\rightarrow$} We executed each project's
test suite for three times to identify projects containing flaky tests
and to ignore these tests (\ie, using the \CodeIn{@Ignore} annotation
from JUnit) to avoid introducing noise in our experiments.  Our final
set of subjects consists of \numSubjs{} projects.

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.25\textwidth]{plots/subjs.pdf}
    \caption{\label{fig:subjects}We fetched \SubjectsGithub{} popular
    projects hosted on \github{}. From this initial sample, we ignored
    \SubjectsGithubNotMaven{} projects without Maven support,
    \SubjectsGithubNotTestable{} untestable projects\Comment{, and
    \SubjectsGithubFlaky{} projects with flaky tests}. We considered
    \numSubjs{} projects to conduct our study.}
\end{figure}

@@

\begin{figure}[h!]
\centering
\resizebox{.48\textwidth}{!}{%
\begin{tabular}{llrrl}
\toprule
\emph{Group} & \emph{Subject} & \multicolumn{1}{c}{$T_s$} & \multicolumn{1}{c}{$T_p$} & $T_s/T_p$ \\%
\midrule%
Medium & BounceStorage \textbf{Chaos} HTTP Proxy  & 1.51m & 1.47m & 
    \cellcolor{lightgray}1.02x\\%
Medium & Apache \textbf{Flink} & 11.79m & 2.57m & 4.59x\\%
Long & Jenkins CI \textbf{Gerrit} Plugin & 51.19m & 40.31m &  1.26x\\%
Medium & Spotify \textbf{Helios} & 4.46m & 1.63m & 2.73x\\%  
Medium & \textbf{Javaslang} & 2.18m & 1.82m & 1.19x\\%
Medium & \textbf{Jcabi} GitHub & 2.76m & 0.30m &
    \cellcolor{lightgray}9.2x\\%
Medium & Hazelcast \textbf{Jet} & 8.26m & 3.67m & 2.25x\\%
Medium & Apache \textbf{Log4J2} & 8.24m & 8.21m & 
    \cellcolor{lightgray}1.00x\\%
Medium & Jankotek \textbf{MapDB} & 10.06m & 8.58m & 1.17x\\%
\midrule
\textbf{average} &  &  &  & \avgSpeedup{}x\\
\bottomrule%
\end{tabular}}
\caption{Speedup (or slowdown) of parallel execution ($T_p$) over
  sequential execution ($T_s$).  Default parallel configuration of
  Maven is used.  Abbreviation of project names appear in bold face
  and highest slowdown/speedup appear in gray color.}
\label{tab:speedup}
\end{figure}
